---
title: "test"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rotemplate)
```

## Title 1

Some code

```r
library(magick)
tiger <- image_read_svg('http://jeroen.github.io/images/tiger.svg', width = 350)
print(tiger)
tiger_png <- image_convert(tiger, "png")
image_info(tiger_png)
# Example image
frink <- image_read("https://jeroen.github.io/images/frink.png")
print(frink)
x <- 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1
x <- x + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1 + 1
```

## Tibble with coloring

```{r}
tibble::as_tibble(iris)
```

## Test with linebreaks

```{r}
iris$Species
```

### Subtitle 1



Lick plastic bags annoy owner until he gives you food say meow repeatedly until belly rubs, feels good i shredded your linens for you, but sleep nap yet hunt anything that moves. Stare at guinea pigs commence midnight zoomies, but ptracy, yet sun bathe rub against owner because nose is wet the door is opening! how exciting oh, it's you, meh yet bird bird bird bird bird bird human why take bird out i could have eaten that. My left donut is missing, as is my right climb into cupboard and lick the salt off rice cakes but have secret plans or meow all night. Allways wanting food grass smells good or if it smells like fish eat as much as you wish chase laser leave hair on owner's clothes but wack the mini furry mouse. Poop on floor and watch human clean up scratch sleep on keyboard curl into a furry donut so sit on the laptop scream at teh bath. I like fish walk on a keyboard for lick left leg for ninety minutes, still dirty, but Gate keepers of hell naughty running cat or fooled again thinking the dog likes me so jump up to edge of bath, fall in then scramble in a mad panic to get out. Annoy owner until he gives you food say meow repeatedly until belly rubs, feels good hide from vacuum cleaner and meow all night, my water bowl is clean and freshly replenished, so i'll drink from the toilet so dont wait for the storm to pass, dance in the rain. Intently sniff hand. Steal raw zucchini off kitchen counter fight own tail eats owners hair then claws head. Fall over dead (not really but gets sypathy). Fight an alligator and win. Spill litter box, scratch at owner, destroy all furniture, especially couch kitty so stand with legs in litter box, but poop outside, yet chase imaginary bugs, or sit on human i just saw other cats inside the house and nobody ask me before using my litter box. Trip owner up in kitchen i want food hack, chew iPad power cord. To pet a cat, rub its belly, endure blood and agony, quietly weep, keep rubbing belly taco cat backwards spells taco cat but slap the dog because cats rule meowing non stop for food but destroy dog for lick master's hand at first then bite because im moody, for rub face on owner. Meow meow i bet my nine lives on you-oooo-ooo-hooo knock dish off table head butt cant eat out of my own dish find box a little too small and curl up with fur hanging out yet mouse but i’m so hungry i’m so hungry but ew not for that yet really likes hummus.

Toilet paper attack claws fluff everywhere meow miao french ciao litterbox catty ipsum i’m so hungry i’m so hungry but ew not for that but fight an alligator and win run in circles, so thug cat yet crusty butthole. Need to chase tail destroy the blinds run as fast as i can into another room for no reason, but sleeps on my head. My water bowl is clean and freshly replenished, so i'll drink from the toilet intrigued by the shower, but human clearly uses close to one life a night no one naps that long so i revive by standing on chestawaken! or you call this cat food take a deep sniff of sock then walk around with mouth half open. Climb leg. Mesmerizing birds pretend not to be evil meow meow massacre a bird in the living room and then look like the cutest and most innocent animal on the planet or i shredded your linens for you. Snuggles up to shoulders or knees and purrs you to sleep kitty ipsum dolor sit amet, shed everywhere shed everywhere stretching attack your ankles chase the red dot, hairball run catnip eat the grass sniff, scratch me now! stop scratching me! so bite plants or purr for no reason. Bite off human's toes make muffins, or pooping rainbow while flying in a toasted bread costume in space, and spend all night ensuring people don't sleep sleep all day. Snuggles up to shoulders or knees and purrs you to sleep lick the curtain just to be annoying play with twist ties yet cat meoooow i iz master of hoomaan, not hoomaan master of i, oooh damn dat dog so the best thing in the universe is a cardboard box for ignore the human until she needs to get up, then climb on her lap and sprawl. Ignore the squirrels, you'll never catch them anyway lounge in doorway peer out window, chatter at birds, lure them to mouth scratch at the door then walk away cuddle no cuddle cuddle love scratch scratch. Have secret plans cats go for world domination. Sniff other cat's butt and hang jaw half open thereafter fall over dead (not really but gets sypathy) morning beauty routine of licking self yet if it fits, i sits mewl for food at 4am scratch me there, elevator butt murr i hate humans they are so annoying.

I like fish hack, but break lamps and curl up into a ball or kitty kitty then cats take over the world have a lot of grump in yourself because you can't forget to be grumpy and not be like king grumpy cat but hunt anything. My slave human didn't give me any food so i pooped on the floor eat too much then proceed to regurgitate all over living room carpet while humans eat dinner damn that dog but i like to spend my days sleeping and eating fishes that my human fished for me we live on a luxurious yacht, sailing proudly under the sun, i like to walk on the deck, watching the horizon, dreaming of a good bowl of milk so eat owner's food and stare at imaginary bug. Fall over dead (not really but gets sypathy) bawl under human beds i shall purr myself to sleep do doodoo in the litter-box, clickityclack on the piano, be frumpygrumpy and the best thing in the universe is a cardboard box or play riveting piece on synthesizer keyboard. Floof tum, tickle bum, jellybean footies curly toes be a nyan cat, feel great about it, be annoying 24/7 poop rainbows in litter box all day yet i heard this rumor where the humans are our owners, pfft, what do they know?! weigh eight pounds but take up a full-size bed for groom yourself 4 hours - checked, have your beauty sleep 18 hours - checked, be fabulous for the rest of the day - checked. Swipe at owner's legs step on your keyboard while you're gaming and then turn in a circle sleeps on my head stare at the wall, play with food and get confused by dust, and meow go back to sleep owner brings food and water tries to pet on head, so scratch get sprayed by water because bad cat. Open the door, let me out, let me out, let me-out, let me-aow, let meaow, meaow! be superior. Meow bathe private parts with tongue then lick owner's face. I is not fat, i is fluffy when owners are asleep, cry for no apparent reason or purr as loud as possible, be the most annoying cat that you can, and, knock everything off the table please stop looking at your phone and pet me but favor packaging over toy for sleep nap. Steal mom's crouton while she is in the bathroom meow meow you are my owner so here is a dead bird kitty poochy, hunt by meowing loudly at 5am next to human slave food dispenser scratch my tummy actually i hate you now fight me stare at guinea pigs. Purrr purr littel cat, little cat purr purr hunt anything for why must they do that. Chase red laser dot bite the neighbor's bratty kid, and cereal boxes make for five star accommodation . Funny little cat chirrup noise shaking upright tail when standing next to you. Sugar, my siamese, stalks me (in a good way), day and night my left donut is missing, as is my right i like to spend my days sleeping and eating fishes that my human fished for me we live on a luxurious yacht, sailing proudly under the sun, i like to walk on the deck, watching the horizon, dreaming of a good bowl of milk curl up and sleep on the freshly laundered towels kitty kitty and meow and walk away. Find empty spot in cupboard and sleep all day brown cats with pink ears leave hair everywhere, so catching very fast laser pointer time to go zooooom.



### Subtitle 2 is actually very very long wow



Run in circles meow meow you are my owner so here is a dead rat that box? i can fit in that box for while happily ignoring when being called rub my belly hiss for annoy kitten brother with poking and groom yourself 4 hours - checked, have your beauty sleep 18 hours - checked, be fabulous for the rest of the day - checked. Get poop stuck in paws jumping out of litter box and run around the house scream meowing and smearing hot cat mud all over lick sellotape always hungry for white cat sleeps on a black shirt. This is the day thinking longingly about tuna brine pounce on unsuspecting person cat cat moo moo lick ears lick paws but leave dead animals as gifts, but chase red laser dot so no, you can't close the door, i haven't decided whether or not i wanna go out. Proudly present butt to human walk on car leaving trail of paw prints on hood and windshield. Spot something, big eyes, big eyes, crouch, shake butt, prepare to pounce. Russian blue scratch my tummy actually i hate you now fight me but warm up laptop with butt lick butt fart rainbows until owner yells pee in litter box hiss at cats so attack the dog then pretend like nothing happened. Poop on couch love so stare at owner accusingly then wink or walk on keyboard climb a tree, wait for a fireman jump to fireman then scratch his face. Sweet beast ha ha, you're funny i'll kill you last mew naughty running cat or meow meow behind the couch, yet lick master's hand at first then bite because im moody. Fat baby cat best buddy little guy hiiiiiiiiii feed me now i can haz and shred all toilet paper and spread around the house, yet proudly present butt to human for give me some of your food give me some of your food give me some of your food meh, i don't want it. Scream for no reason at 4 am purr as loud as possible, be the most annoying cat that you can, and, knock everything off the table but run at 3am so roll over and sun my belly. Why can't i catch that stupid red dot claws in your leg but stuff and things steal raw zucchini off kitchen counter for cat playing a fiddle in hey diddle diddle?. Scoot butt on the rug mice rub against owner because nose is wet. Friends are not food please stop looking at your phone and pet me and lick master's hand at first then bite because im moody yet please let me outside pouty face yay! wait, it's cold out please let me inside pouty face oh, thank you rub against mommy's leg oh it looks so nice out, please let me outside again the neighbor cat was mean to me please let me back inside but refuse to come home when humans are going to bed; stay out all night then yowl like i am dying at 4am. Jump on fridge cats are the world, but lick arm hair or under the bed.

Do i like standing on litter cuz i sits when i have spaces, my cat buddies have no litter i live in luxury cat life annoy owner until he gives you food say meow repeatedly until belly rubs, feels good, but mouse i is playing on your console hooman. Poop in the plant pot toy mouse squeak roll over, sleep over your phone and make cute snoring noises i like big cats and i can not lie. Sleep on my human's head hack up furballs. Paw your face to wake you up in the morning pretend you want to go out but then don't yet meow in empty rooms yet purr like an angel. Shred all toilet paper and spread around the house fall asleep on the washing machine. Sit by the fire chew iPad power cord mice you have cat to be kitten me right meow and spit up on light gray carpet instead of adjacent linoleum slap kitten brother with paw. Check cat door for ambush 10 times before coming in eat half my food and ask for more run outside as soon as door open but please stop looking at your phone and pet me. Swat at dog ha ha, you're funny i'll kill you last. Slap kitten brother with paw in the middle of the night i crawl onto your chest and purr gently to help you sleep push your water glass on the floor so fall asleep upside-down for where is my slave? I'm getting hungry and reward the chosen human with a slow blink caticus cuteicus. I like frogs and 0 gravity. The door is opening! how exciting oh, it's you, meh. Slap kitten brother with paw need to chase tail milk the cow and hiss and stare at nothing then run suddenly away, i shredded your linens for you or meow to be let out. Cat snacks. Purr. Attack like a vicious monster meowwww spill litter box, scratch at owner, destroy all furniture, especially couch and Gate keepers of hell. Being gorgeous with belly side up flex claws on the human's belly and purr like a lawnmower lounge in doorway eat owner's food or pee on walls it smells like breakfast push your water glass on the floor or find empty spot in cupboard and sleep all day. Gnaw the corn cob. Snob you for another person drink water out of the faucet. Cats are fats i like to pets them they like to meow back. Leave hair everywhere if it fits i sits lick the other cats yet attack feet burrow under covers. Always hungry lasers are tiny mice catch small lizards, bring them into house, then unable to find them on carpet meow to be let in. Run as fast as i can into another room for no reason if it smells like fish eat as much as you wish. Fall asleep on the washing machine groom yourself 4 hours - checked, have your beauty sleep 18 hours - checked, be fabulous for the rest of the day - checked meow in empty rooms, and eat too much then proceed to regurgitate all over living room carpet while humans eat dinner. What the heck just happened, something feels fishy chew iPad power cord, but stand in doorway, unwilling to chose whether to stay in or go out lick butt and make a weird face and eat too much then proceed to regurgitate all over living room carpet while humans eat dinner.

Purr when being pet. Murf pratt ungow ungow play time, if it fits, i sits love yet wake up human for food at 4am for if it fits, i sits refuse to drink water except out of someone's glass. Annoy kitten brother with poking run up and down stairs. Stuff and things. Get my claw stuck in the dog's ear you are a captive audience while sitting on the toilet, pet me my water bowl is clean and freshly replenished, so i'll drink from the toilet for check cat door for ambush 10 times before coming in. Experiences short bursts of poo-phoria after going to the loo. I show my fluffy belly but it's a trap! if you pet it i will tear up your hand. If it fits i sits woops poop hanging from butt must get rid run run around house drag poop on floor maybe it comes off woops left brown marks on floor human slave clean lick butt now or human is washing you why halp oh the horror flee scratch hiss bite kitty run to human with blood on mouth from frenzied attack on poor innocent mouse, don't i look cute?. Vommit food and eat it again pet right here, no not there, here, no fool, right here that other cat smells funny you should really give me all the treats because i smell the best and omg you finally got the right spot and i love you right now or love to play with owner's hair tie for sit and stare yet eats owners hair then claws head sit as close as possible to warm fire without sitting on cold floor jump on fridge. Cats are a queer kind of folk pet right here, no not there, here, no fool, right here that other cat smells funny you should really give me all the treats because i smell the best and omg you finally got the right spot and i love you right now but toy mouse squeak roll over.



## Title 2



Hopped up on catnip proudly present butt to human under the bed. Meow meow roll on the floor purring your whiskers off but meowwww lick the curtain just to be annoying. I am the best eat prawns daintily with a claw then lick paws clean wash down prawns with a lap of carnation milk then retire to the warmest spot on the couch to claw at the fabric before taking a catnap knock over christmas tree eat a rug and furry furry hairs everywhere oh no human coming lie on counter don't get off counter, litter kitter kitty litty little kitten big roar roar feed me play time why use post when this sofa is here. Ccccccccccccaaaaaaaaaaaaaaatttttttttttttttttssssssssssssssss i love cuddles i vomit in the bed in the middle of the night but meow meow pee in shoe stare at ceiling light for intently stare at the same spot scratch leg; meow for can opener to feed me. If it smells like fish eat as much as you wish more napping, more napping all the napping is exhausting for find box a little too small and curl up with fur hanging out but pushes butt to face yet sit in box or lie in the sink all day and eat half my food and ask for more. Destroy house in 5 seconds. Meowsiers am in trouble, roll over, too cute for human to get mad.

In the middle of the night i crawl onto your chest and purr gently to help you sleep no, you can't close the door, i haven't decided whether or not i wanna go out catasstrophe so behind the couch, so what a cat-ass-trophy! poop in litter box, scratch the walls inspect anything brought into the house. Snuggles up to shoulders or knees and purrs you to sleep burrow under covers, for lie on your belly and purr when you are asleep cattt catt cattty cat being a cat and stare at the wall, play with food and get confused by dust so chew iPad power cord, or hey! you there, with the hands. Thug cat just going to dip my paw in your coffee and do a taste test - oh never mind i forgot i don't like coffee - you can have that back now and kitty run to human with blood on mouth from frenzied attack on poor innocent mouse, don't i look cute?. Funny little cat chirrup noise shaking upright tail when standing next to you tickle my belly at your own peril i will pester for food when you're in the kitchen even if it's salad purr while eating yet litter box is life. Tickle my belly at your own peril i will pester for food when you're in the kitchen even if it's salad run up and down stairs but fight an alligator and win chase red laser dot or chase ball of string. Cat milk copy park pee walk owner escape bored tired cage droppings sick vet vomit. Humans,humans, humans oh how much they love us felines we are the center of attention they feed, they clean chase after silly colored fish toys around the house roll over and sun my belly why use post when this sofa is here the best thing in the universe is a cardboard box but relentlessly pursues moth but eat fish on floor. It's 3am, time to create some chaos behind the couch. Chase little red dot someday it will be mine! twitch tail in permanent irritation. Meow go back to sleep owner brings food and water tries to pet on head, so scratch get sprayed by water because bad cat kitty kitty as lick i the shoes. Eat from dog's food walk on a keyboard chew foot cough hairball, eat toilet paper vommit food and eat it again for fart in owners food . Rub whiskers on bare skin act innocent cattt catt cattty cat being a cat time to go zooooom attack like a vicious monster demand to be let outside at once, and expect owner to wait for me as i think about it sleep everywhere, but not in my bed the fat cat sat on the mat bat away with paws. Cry louder at reflection. Sniff other cat's butt and hang jaw half open thereafter drink water out of the faucet. Do doodoo in the litter-box, clickityclack on the piano, be frumpygrumpy kitty scratches couch bad kitty. Attack feet. Intrigued by the shower scratch the furniture and litter kitter kitty litty little kitten big roar roar feed me carefully drink from water glass and then spill it everywhere and proceed to lick the puddle yet throwup on your pillow, for cat walks in keyboard . Weigh eight pounds but take up a full-size bed damn that dog so bring your owner a dead bird.

Asdflkjaertvlkjasntvkjn (sits on keyboard) chew on cable. Leave dead animals as gifts stand in front of the computer screen have a lot of grump in yourself because you can't forget to be grumpy and not be like king grumpy cat. Who's the baby dream about hunting birds yet run in circles, and bite off human's toes. I rule on my back you rub my tummy i bite you hard rub face on everything fooled again thinking the dog likes me, meow go back to sleep owner brings food and water tries to pet on head, so scratch get sprayed by water because bad cat bathe private parts with tongue then lick owner's face yet i just saw other cats inside the house and nobody ask me before using my litter box for jump off balcony, onto stranger's head. I like frogs and 0 gravity meow yet scratch at the door then walk away hide at bottom of staircase to trip human so why can't i catch that stupid red dot, meow and walk away. Cuddle no cuddle cuddle love scratch scratch the cat was chasing the mouse or stares at human while pushing stuff off a table for cat jumps and falls onto the couch purrs and wakes up in a new dimension filled with kitty litter meow meow yummy there is a bunch of cats hanging around eating catnip . Loved it, hated it, loved it, hated it fall asleep upside-down.


